Appendix

### 2020-05-21 appendix/appendixV5.Rmd
commit 3 05/20

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
    scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, hjust = 1),
          axis.text.x = element_text(size = .7*lsize, hjust = 1.1),
          plot.caption = element_text(size=lsize))
  return(p)
}
```

@@

f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
               labels = c("ExpPC x N", 
                          "ExpPC x K", 
                          "logExpPC x N", 
                          'logExpPC x logN', 
                          'PCTGDP x N',
                          'PCTGDP x logN',
                          'PCTGDP x K'),
               ncol = 2, nrow = 4, 
               font.label = list(size=13, face = 'bold'),
               hjust = 0)
ggsave("./plots/fig.pdf", plot = f, width = 21, height = 29, units = "cm")

f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
               labels = c("ExpPC x N", 
                          "ExpPC x K", 
                          "logExpPC x N", 
                          'logExpPC x logN', 
                          'PCTGDP x N',
                          'PCTGDP x logN',
                          'PCTGDP x K'),
               ncol = 3, nrow = 3, 
               font.label = list(size=13, face = 'bold'),
               hjust = 0)
ggsave("./plots/fig2.pdf", plot = f, width = 29, height = 21, units = "cm")

>>>>

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
    scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, hjust = 1),
          axis.text.x = element_text(size = .7*lsize, hjust = 1.1),
          plot.caption = element_text(size=lsize)) + 
    theme(panel.grid.major = element_blank())
  return(p)
}
```

@@

f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
               labels = c("ExpPC x N", 
                          "ExpPC x K", 
                          "logExpPC x N", 
                          'logExpPC x logN', 
                          'PCTGDP x N',
                          'PCTGDP x logN',
                          'PCTGDP x K'),
               ncol = 2, nrow = 4, 
               font.label = list(size=13, face = 'bold'),
               hjust = 0)
ggsave("./plots/fig3.pdf", plot = f, width = 21, height = 29, units = "cm")

f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
               labels = c("ExpPC x N", 
                          "ExpPC x K", 
                          "logExpPC x N", 
                          'logExpPC x logN', 
                          'PCTGDP x N',
                          'PCTGDP x logN',
                          'PCTGDP x K'),
               ncol = 3, nrow = 3, 
               font.label = list(size=13, face = 'bold'),
               hjust = 0)
ggsave("./plots/fig4.pdf", plot = f, width = 29, height = 21, units = "cm")
